\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-03 smurf_paper.tex
Remove the masking alternative to gap filling since it is not used by default

The evaluation of the \model{FLT} model (Section~\ref{sec:flt})
involves taking the Fast Fourier Transform (FFT) of each bolometer
time series. Data that have been flagged as bad for any reason (for
instance, due to the presence of spikes, steps, or unusual common-mode
signal) need to be excluded from this FFT. Two methods are available:

\begin{itemize}
\item Gap-filling: each contiguous block of bad data samples is filled
with artificial data before taking the FFT. A least squares linear fit is
performed to the 50 samples preceding the block, and a similar fit is
performed to the 50 samples following the block. These are used to
estimate the expected values at the start and end of the block of bad
values. The bad values are then replaced by linear interpolation between
the expected start and end values. Gaussian noise is added with a
standard deviation equal to the mean of the RMS residuals in the two
fits.

\item Masking: each bad data value is replaced by zero, and an
associated mask is created that holds 1.0 for each good sample in the
time stream and 0.0 for each bad sample. The masked data and the mask
are then each filtered in the same way using FFTs, and the filtered
data are finally normalised by dividing them by the filtered mask.
\end{itemize}

>>>>

The evaluation of the \model{FLT} model (Section~\ref{sec:flt}) involves
taking the Fast Fourier Transform (FFT) of each bolometer time series.
Data that have been flagged as bad for any reason (for instance, due to
the presence of spikes, steps, or unusual common-mode signal) need to be
excluded from this FFT. For this reason, each contiguous block of bad
data samples is filled with artificial data before taking the FFT. A
least squares linear fit is performed to the 50 samples preceding the
block, and a similar fit is performed to the 50 samples following the
block. These are used to estimate the expected values at the start and
end of the block of bad values. The bad values are then replaced by
linear interpolation between the expected start and end values. Gaussian
noise is added with a standard deviation equal to the mean of the RMS
residuals in the two fits.
